Friends Get More Money, Attention, and Handshakes: Xinhua, Diplomacy, and Chinese Foreign Aid

### 2022-06-14 04_paper/Draft2.Rmd
william & mary draft

---
title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    number_sections: yes
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_Xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

@@

In this study, we tackle this question by considering complementarities between where China gives aid with Chinese media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic activities. These measures capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China's development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData's Chinese development finance dataset with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China's broader diplomacy and legitimacy seeking objectives on the world stage.

>>>>

---
title: "Friends Get More Money, Attention, and Handshakes: Xinhua, Diplomacy, and Chinese Foreign Aid"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    number_sections: yes
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_Xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

@@

In this study, we tackle this question by exploiting new data on Chinese state-run media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic visits. These measures capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China's development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData's Chinese development finance dataset with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China's broader diplomacy and legitimacy seeking objectives on the world stage.
